Paper_text_working_file

### 2019-04-28 Paper_markdown.Rmd
Data generation and mutation complete

install.packages("tidyverse")

library(plyr)
library(tidyverse)
library(haven)

@@

>>>>

install.packages("tidyverse")
install.packages("DataCombine")

library(plyr)
library(tidyverse)
library(DataCombine)
library(haven)

@@

#Creating a variable which only identifies if a mid occured in that dyad-year
head(Master3$hihost, 1000)
Master3 <- Master3 %>%
    mutate(Mid = ifelse(is.na(hihost), 0, 1))
head(Master3$Mid, 1000)

#Creating a variable which only identifies if a Mid which involved the use of force occured in that dyad-year.
head(Master3$hihost, 1000)
Master3 <- Master3 %>%
    mutate(Use_Force = ifelse(hihost > 3, 1, 0))
Master3$Use_Force[is.na(Master3$Use_Force)] <- 0
head(Master3$Use_Force, 1000)

#Creating variable identifying joint democracy
Master3 <- Master3 %>%
    mutate(Joint_Dem = ifelse(politya >= 6 & polityb >=6, 1, 0))
head(Master3$Joint_Dem, 1000)

#Creating variable measuring relative capabilities
Master3 <- filter(Master3, cinca != -9, cincb != -9)
Master3 <- Master3 %>%
    mutate(Relative_Cap = cinca/(cinca+cincb))
head(Master3$Relative_Cap, 1000)

#Creating variable identifying if at least one member of the dyad is a major power.
Master3 <- Master3 %>%
    mutate(Joint_Dem = ifelse(majpow1 == 1 | majpow2 == 1, 1, 0))
head(Master3$Joint_Dem, 1000)

#Creating a variable identifying if the dyad had experienced a MID in the previous two years.
Master3 <- slide(Master3, Var = "Mid", GroupVar = "" slideBy = -2)

#Variable identfying the presence of an alliance between the two members of the dyad
Master3 <- Master3 %>%
    mutate(Ally = ifelse(atopally ==1, 1, 0))
Master3$Ally[is.na(Master3$Ally)] <- 0
head(Master3$Ally, 1000)

#Variable identifying if the two members of the dyad are in the same region
Master3 <- Master3 %>%
    mutate(Same_Region = ifelse(region1 == region2, 1, 0))
head(Master3$Same_Region, 1000)

#Creating a naval capability variable by modifying the systemic proportion of naval tonnage held by the US
Master3 <- Master3 %>%
    mutate(US_Naval_Cap =(milex/milper)*tonn_prop) 
Master3 <- Master3 %>%
    mutate(US_Naval_Cap = (US_Naval_Cap/10000)) 
head(Master3$US_Naval_Cap, 1000)
